Nearest Neighbour Methods for Length of Stay Prediction

### 2015-02-04 papers/paper.tex
Move feature selection into its own section, add subheadings

In Section \ref{sec:nn}, we outline the basics of nearest neighbour
classification and describe both the existing K* extension and our proposed
extension, Ranked Distance. Section \ref{sec:eval} describes the method used
to evaluate the performance of these classifiers, and Section \ref{sec:results}
proceeds to discuss the results. We present concluding remarks in Section
\ref{sec:conclusions}.

\section{Nearest Neighbour Classification}
\label{sec:nn}
In this section we will describe the $k$-nearest neighbour ($k$-NN) algorithm
and discuss some extensions which we use in our work. Additionally, we will
describe our contribution, which is an extension of the distance metric for
finding the nearest neighbours.

\subsection{Basic Algorithm}
The $k$-nearest neighbour classifier is an example of an
\textit{instance-based} learning algorithm. This is because it does not, unlike
the other classifiers described in this section, attempt to deduce or
generalise a relationship between the features and the class: it simply stores
all training examples and classifies an unseen example by finding the $k$
``nearest'' examples (or \textit{instances}) and assigning the majority class
to the new example. In the simplest form of the algorithm, $k$ is chosen to be
1 and the Euclidean distance is used to measure the closeness of neighbours:
\begin{equation*}
\mathrm{Distance} = \sqrt{(x_1-y_1)^2 + (x_2-y_2)^2 + \ldots + (x_n-y_n)^2}
\end{equation*}
where $x_i,y_i$ are the values of the $i$-th feature for two different feature
vectors (or instances).

@@

\subsection{Feature Selection}
Here we introduce the feature selection algorithms we evaluate in our work.
Several of these have not been investigated in previous work on length of
stay prediction.

\subsubsection{Pearson Correlation Coefficient}
The Pearson correlation coefficient measures the degree of linear correlation
between two variables. It is always in the range $[-1,1]$, where -1 is total
negative correlation, 0 is no (linear) correlation, and 1 is total positive
correlation. We compute the Pearson correlation between each feature and the
class using:
\begin{equation*}
r_i = \dfrac{\sum_{i=1}^m (x_i-\bar{x})(c-\bar{c})}{\sqrt{(\sum_{i=1}^m x_i-\bar{x})(\sum_{i=1}^m c-\bar{c})}}
\end{equation*}
where $m$ is the number of training examples, $x_i$ is the value of feature
$i$, and $\bar{x}$ and $\bar{c}$ are the arithmetic averages of the feature
values and the class values respectively.

@@

>>>>

In Section \ref{sec:nn}, we outline the basics of nearest neighbour
classification and describe both the existing K* extension and our proposed
extension, Ranked Distance. Section \ref{sec:features} outlines the feature
selection methods we used. Section \ref{sec:eval} describes the method used
to evaluate the performance of these classifiers, and Section \ref{sec:results}
proceeds to discuss the results. We present concluding remarks in Section
\ref{sec:conclusions}.

\section{Nearest Neighbour Classification}
\label{sec:nn}

\subsection{Basic Algorithm}
The $k$-nearest neighbour classifier is an example of an
\textit{instance-based} learning algorithm. This is because it does not attempt
to deduce or
generalise a relationship between the features and the class: it simply stores
all training examples and classifies an unseen example by finding the $k$
``nearest'' examples (or \textit{instances}) and assigning the majority class
to the new example. In the simplest form of the algorithm, $k$ is chosen to be
1 and the Euclidean distance is used to measure the closeness of neighbours:
\begin{equation*}
\mathrm{Distance} = \sqrt{(x_1-y_1)^2 + (x_2-y_2)^2 + \ldots + (x_n-y_n)^2}
\end{equation*}
where $x_i,y_i$ are the values of the $i$-th feature for two different feature
vectors (or instances).

@@

\section{Feature Selection}
\label{sec:features}
Here we introduce the feature selection algorithms we evaluate in our work.
Several of these have not been investigated in previous work on length of
stay prediction.

\subsection{Automatic Selection}
\subsubsection{Pearson Correlation Coefficient}
The Pearson correlation coefficient measures the degree of linear correlation
between two variables. It is always in the range $[-1,1]$, where -1 is total
negative correlation, 0 is no (linear) correlation, and 1 is total positive
correlation. We compute the Pearson correlation between each feature and the
class using:
\begin{equation*}
r_i = \dfrac{\sum_{i=1}^m (x_i-\bar{x})(c-\bar{c})}{\sqrt{(\sum_{i=1}^m x_i-\bar{x})(\sum_{i=1}^m c-\bar{c})}}
\end{equation*}
where $m$ is the number of training examples, $x_i$ is the value of feature
$i$, and $\bar{x}$ and $\bar{c}$ are the arithmetic averages of the feature
values and the class values respectively.

@@

\subsection{Manual Selection}

\subsection{Discretisation}
